A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-11-06 latex/main.tex
Comment out unnecessary Cell stuff

\section*{RESOURCE AVAILABILITY}

%%%  The resource availability section is required
%%%  for all research articles. This component
%%%  has 3 subsections: "lead contact," "materials
%%%  availability," and "data and code availability."
%%%  All 3 subsections must be included, even if no
%%%  unique materials were generated in the study.
%%%  Do not edit or change the names of the subheadings.
%%%  No other subheadings or text are allowed in the
%%%  resource availability section.

\subsection*{Lead contact}

%%%  Authors are required to designate a lead contact,
%%%  who will be responsible for communication with
%%%  the journal before and after publication and is
%%%  the arbiter of disputes, including concerns
%%%  related to reagents or resource sharing. Only
%%%  one author can be named the lead contact, and
%%%  only the lead contact’s information may be
%%%  provided in this section.

Requests for further information and resources
should be directed to and will be fulfilled
by the lead contact, XX (XX@university.edu).

\subsection*{Materials availability}

%%%  This subsection must include a statement describing
%%%  the availability of newly generated materials
%%%  associated with the paper, including any conditions
%%%  for access. If there are no newly generated materials
%%%  associated with the paper, the statement should
%%%  state this, e.g.: This study did not generate new
%%%  materials.

This study did not generate new materials.

@@

\section*{AUTHOR CONTRIBUTIONS}

%%%  This component is required for most research papers.
%%%  Mention each individual author with a statement
%%%  outlining the contribution of each author to the work.

Conceptualization, S.C.P. and S.Y.W.;
methodology, A.B., S.C.P., and S.Y.W.;
investigation, M.E., A.N.V., N.A.V., S.C.P., and S.Y.W.;
writing-–original draft, S.C.P. and S.Y.W.;
writing-–review \& editing, S.C.P. and S.Y.W.;
funding acquisition, S.C.P. and S.Y.W.;
resources, M.E.V and C.K.B.;
supervision, A.B., N.L.W., and A.A.D.

\section*{DECLARATION OF INTERESTS}

%%%  This component is required for all articles, even
%%%  if the authors have no competing interests; if
%%%  this is the case, insert "The authors declare no
%%%  competing interests." Please refer to the
%%%  declaration of interests policy:
%%%  https://www.cell.com/declaration-of-interests

% TODO: Close https://github.com/jeromekelleher/sc2ts-paper/issues/922
The authors declare no competing interests.

\section*{DECLARATION OF GENERATIVE AI AND AI-ASSISTED TECHNOLOGIES}

%%%  If generative AI and AI-assisted technologies
%%%  were used in the writing process, this must
%%%  be disclosed in the paper. This declaration
%%%  does not apply to the use of basic tools for
%%%  checking grammar, spelling, references, etc.
%%%  If you have nothing to disclose, please do not
%%%  include this component.

During the preparation of this work, the author(s) used ChatGPT
in order to obtain editorial input on the text.
After using this tool or service, the author(s) reviewed
and edited the content as needed and take(s) full responsibility for the content of the publication.

>>>>

% \section*{RESOURCE AVAILABILITY}

% %%%  The resource availability section is required
% %%%  for all research articles. This component
% %%%  has 3 subsections: "lead contact," "materials
% %%%  availability," and "data and code availability."
% %%%  All 3 subsections must be included, even if no
% %%%  unique materials were generated in the study.
% %%%  Do not edit or change the names of the subheadings.
% %%%  No other subheadings or text are allowed in the
% %%%  resource availability section.

% \subsection*{Lead contact}

% %%%  Authors are required to designate a lead contact,
% %%%  who will be responsible for communication with
% %%%  the journal before and after publication and is
% %%%  the arbiter of disputes, including concerns
% %%%  related to reagents or resource sharing. Only
% %%%  one author can be named the lead contact, and
% %%%  only the lead contact’s information may be
% %%%  provided in this section.

% Requests for further information and resources
% should be directed to and will be fulfilled
% by the lead contact, XX (XX@university.edu).

% \subsection*{Materials availability}

% %%%  This subsection must include a statement describing
% %%%  the availability of newly generated materials
% %%%  associated with the paper, including any conditions
% %%%  for access. If there are no newly generated materials
% %%%  associated with the paper, the statement should
% %%%  state this, e.g.: This study did not generate new
% %%%  materials.

% This study did not generate new materials.

@@

% \section*{AUTHOR CONTRIBUTIONS}

% %%%  This component is required for most research papers.
% %%%  Mention each individual author with a statement
% %%%  outlining the contribution of each author to the work.

% Conceptualization, S.C.P. and S.Y.W.;
% methodology, A.B., S.C.P., and S.Y.W.;
% investigation, M.E., A.N.V., N.A.V., S.C.P., and S.Y.W.;
% writing-–original draft, S.C.P. and S.Y.W.;
% writing-–review \& editing, S.C.P. and S.Y.W.;
% funding acquisition, S.C.P. and S.Y.W.;
% resources, M.E.V and C.K.B.;
% supervision, A.B., N.L.W., and A.A.D.

% \section*{DECLARATION OF INTERESTS}

% %%%  This component is required for all articles, even
% %%%  if the authors have no competing interests; if
% %%%  this is the case, insert "The authors declare no
% %%%  competing interests." Please refer to the
% %%%  declaration of interests policy:
% %%%  https://www.cell.com/declaration-of-interests

% % TODO: Close https://github.com/jeromekelleher/sc2ts-paper/issues/922
% The authors declare no competing interests.

% \section*{DECLARATION OF GENERATIVE AI AND AI-ASSISTED TECHNOLOGIES}

% %%%  If generative AI and AI-assisted technologies
% %%%  were used in the writing process, this must
% %%%  be disclosed in the paper. This declaration
% %%%  does not apply to the use of basic tools for
% %%%  checking grammar, spelling, references, etc.
% %%%  If you have nothing to disclose, please do not
% %%%  include this component.

% During the preparation of this work, the author(s) used ChatGPT
% in order to obtain editorial input on the text.
% After using this tool or service, the author(s) reviewed
% and edited the content as needed and take(s) full responsibility for the content of the publication.
